Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-04-24 Paper.tex
fix(sec 9.2): Updated the memory expansion cost
The cost of memory expansion is not always proportional to the memory used. For memories above 704 bytes, it approximates the square of the memory used (see eq. 326).

Over an account's execution, the total fee for memory-usage payable is proportional to smallest multiple of 32 bytes that are required such that all memory indices (whether for read or write) are included in the range. This is paid for on a just-in-time basis; as such, referencing an area of memory at least 32 bytes greater than any previously indexed memory will certainly result in an additional memory usage fee. Due to this fee it is highly unlikely addresses will ever go above 32-bit bounds. That said, implementations must be able to manage this eventuality.

>>>>

Over an account's execution, the total fee for memory-usage payable is specified in \ref{app:vm}. If you use a small amount of memory, this fee is proportional to smallest multiple of 32 bytes that are required such that all memory indices (whether for read or write) are included in the range. For larger amounts of memory the fee is approximately the square of that number. See Appendix \label{app:vm} for the exact expression. This is paid for on a just-in-time basis; as such, referencing an area of memory at least 32 bytes greater than any previously indexed memory will result in an additional memory usage fee. Due to this fee it is highly unlikely addresses will ever go above 32-bit bounds. That said, implementations must be able to manage this eventuality.
